# Graphical illustration of the revisions {#sec-Revisions-illustration}

All final revisions to variables considered (but not necessarily included) in the analysis are illustrated in this appendix section with the twofold objective. First, the graphs are useful for illustrating the magnitude of the revisions across variables and countries. Second, the plots are indispensable to potentially identify any issues with the dataset that could impair our analysis (e.g. excessive values or lack of revisions). @sec-code-retrieval of the online appendix provides statistical codes used to retrieve the data.
<!-- APPENDIX BUG CROSS REF : https://github.com/quarto-dev/quarto-cli/issues/3234 -->

## Fiscal revenue variables
```{r}
#| fig-cap: Final revisions to total revenue
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-TOR

targets::tar_read(plot_revision_TOR)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to direct taxes
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-DTX

targets::tar_read(plot_revision_DTX)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to indirect taxes
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-TIN


targets::tar_read(plot_revision_TIN)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to social contributions
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-SCT

targets::tar_read(plot_revision_SCT)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to other current revenue
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-OCR

targets::tar_read(plot_revision_OCR)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to capital revenue
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-KTR

targets::tar_read(plot_revision_KTR)
```

## Fiscal spending variables

```{r}
#| fig-cap: Final revisions to total expenditure
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-TOE

targets::tar_read(plot_revision_TOE)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to social transfers
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-THN

targets::tar_read(plot_revision_THN)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to purchases
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-PUR

targets::tar_read(plot_revision_PUR)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to interest payments
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-INP

targets::tar_read(plot_revision_INP)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to gov. compensation
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-COE

targets::tar_read(plot_revision_COE)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to other current expenditure
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-OCE

targets::tar_read(plot_revision_OCE)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to gov. investment
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-GIN

targets::tar_read(plot_revision_GIN)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to other capital expenditure
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-OKE

targets::tar_read(plot_revision_OKE)
```

## Macro variables

```{r}
#| fig-cap: Final revisions to GDP
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-YEN

targets::tar_read(plot_revision_YEN)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to private consumption
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-PCN

targets::tar_read(plot_revision_PCN)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to total investment
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-ITN

targets::tar_read(plot_revision_ITN)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to exports
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-EXN

targets::tar_read(plot_revision_EXN)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to gov. consumption
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-GCN

targets::tar_read(plot_revision_GCN)
```

::: {.content-visible when-format="pdf"}
\pagebreak
:::

```{r}
#| fig-cap: Final revisions to wages and salaries
#| fig-width: 6.3
#| fig-height: 8
#| label: fig-WGS

targets::tar_read(plot_revision_WGS)
```
