# Graphical illustration of the revisions {#appendix-Revisions-illustration}

All final revisions to variables considered (but not necessarily included) in the analysis are illustrated in this appendix section with the twofold objective. First, the graphs are useful for illustrating the magnitude of the revisions across variables and countries. Second, the plots are indispensable to potentially identify any issues with the dataset that could impair our analysis (e.g. excessive values or lack of revisions). @appendix-code-retrieval of the online appendix provides statistical codes used to retrieve the data.

## Fiscal revenue variables
```{r}
#| fig-cap: Final revisions to total revenue
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-TOR

targets::tar_read(plot_revision_TOR)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to direct taxes
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-DTX

targets::tar_read(plot_revision_DTX)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to indirect taxes
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-TIN


targets::tar_read(plot_revision_TIN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to social contributions
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-SCT

targets::tar_read(plot_revision_SCT)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to other current revenue
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-OCR

targets::tar_read(plot_revision_OCR)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to capital revenue
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-KTR

targets::tar_read(plot_revision_KTR)
```

## Fiscal spending variables

```{r}
#| fig-cap: Final revisions to total expenditure
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-TOE

targets::tar_read(plot_revision_TOE)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to social transfers
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-THN

targets::tar_read(plot_revision_THN)
```

```{r}
#| fig-cap: Final revisions to purchases
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-PUR

targets::tar_read(plot_revision_PUR)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to interest payments
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-INP

targets::tar_read(plot_revision_INP)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to gov. compensation
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-COE

targets::tar_read(plot_revision_COE)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to other current expenditure
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-OCE

targets::tar_read(plot_revision_OCE)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to gov. investment
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-GIN

targets::tar_read(plot_revision_GIN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to other capital expenditure
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-OKE

targets::tar_read(plot_revision_OKE)
```

## Macro variables

```{r}
#| fig-cap: Final revisions to GDP
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-YEN

targets::tar_read(plot_revision_YEN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to private consumption
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-PCN

targets::tar_read(plot_revision_PCN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to total investment
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-ITN

targets::tar_read(plot_revision_ITN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to exports
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-EXN

targets::tar_read(plot_revision_EXN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to gov. consumption
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-GCN

targets::tar_read(plot_revision_GCN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to wages and salaries
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center
#| label: fig-WGS

targets::tar_read(plot_revision_WGS)
```
