All final revisions to variables considered (but not necessarily included) in the analysis are illustrated in this appendix section with the twofold objective. First, the graphs are useful for illustrating the magnitude of the revisions across variables and countries. Second, the plots are indispensable to potentially identify any issues with the dataset that could impair our analysis (e.g. excessive values or lack of revisions). @sec-code-retrieval of the online appendix provides statistical codes used to retrieve the data.

## Fiscal revenue variables
```{r}
#| fig-cap: Final revisions to total revenue
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_TOR)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to direct taxes
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_DTX)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to indirect taxes
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_TIN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to social contributions
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_SCT)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to other current revenue
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_OCR)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to capital revenue
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_KTR)
```

## Fiscal spending variables

```{r}
#| fig-cap: Final revisions to total expenditure
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_TOE)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to social transfers
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_THN)
```

```{r}
#| fig-cap: Final revisions to purchases
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_PUR)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to interest payments
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_INP)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to gov. compensation
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_COE)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to other current expenditure
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_OCE)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to gov. investment
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_GIN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to other capital expenditure
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_OKE)
```

## Macro variables

```{r}
#| fig-cap: Final revisions to GDP
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_YEN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to private consumption
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_PCN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to total investment
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_ITN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to exports
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_EXN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to gov. consumption
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_GCN)
```
\pagebreak

```{r}
#| fig-cap: Final revisions to wages and salaries
#| fig-width: 6.3
#| fig-height: 8
#| fig-align: center

targets::tar_read(plot_revision_WGS)
```
